A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-15 manuscript/manuscript.tex
rewording paragraphs on reviewers advice

Fileset and field specifications are passed to the data specification of
a Study class via the \emph{add\_data\_specs} class attribute as a list
of named \emph{FilesetSpec} and \emph{FieldSpec} objects (Figure \ref{fig:data_spec}).
Specifications for acquired data (i.e. input data to the study) are
distinguished from derived data by using the \emph{FilesetInputSpec}
and \emph{FieldInputSpec} subtypes. However, the distinction is
fluid, with derived specifications able to be overridden by acquired
specifications in subclasses or MultiStudy classes, and vice-versa, or
passed inputs when the class is instantiated.

@@

Pipelines are constructed dynamically by ``pipeline constructor" methods
of the study. Pipeline constructor methods are referenced by name in the \emph{pipeline\_name}
argument of the FilesetSpec and FieldSpec objects of data specifications
they derive. Pipeline constructor methods should only receive wildcard keyword
arguments (e.g. \lstinline{my_pipeline(self, **name_maps)}), and these arguments
should be passed as a dictionary directly to the \emph{name\_maps} argument
of the pipeline initialisation to enable inputs and outputs of the
pipeline to be rerouted to alternative data specifications in modified constructor
methods, typically in subclasses and multi-studies (see
\emph{Extension and specialisation by class inheritance} and \emph{Implementing multi-modal studies}).

@@

Node interfaces are connected to each other, and to inputs and outputs of the pipeline, by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary. The keys of the \emph{inputs} dictionary correspond to
trait names in the node's input interface, whereas the keys of the \emph{outputs} dictionary correspond to
names of entries in the data specification table. The values of both dictionaries are 2-tuples. For pipeline
inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification table
and the format the input is expected in (i.e. a FileFormat for Fileset specifications or Python datatype for Field specifications).
For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output interface and the format the
output data is generated in. For input connections from other nodes, values of the \emph{inputs} dictionary
consist of a reference to the upstream node and the name of a trait in the
upstream node's output interface (output connections to other nodes are implied by input connections of other nodes).

>>>>

Fileset and field specifications of a Study class are defined by the
list of \emph{FilesetSpec} and \emph{FieldSpec} objects in the
\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}),
The specifications are collated with any data specifications in base
classes into the \emph{\_data\_specs} class attribute during the creation
of the class by the StudyMetaClass metaclass.
Specifications for input data to the study are
distinguished from derivative specifications by the \emph{FilesetInputSpec}
and \emph{FieldInputSpec} subtypes. However, the distinction between
input and derived data is somewhat blurred, as derivative specifications can be
passed input data when the class is instantiated. In addition,
when subclassing a Study class, or combining it in a MultiStudy class,
derivative specifications can be overridden by input
specifications, and vice-versa.

@@

Pipelines are constructed dynamically by ``pipeline constructor" methods
of the study. Pipeline constructor methods are referenced by name in the
data specifications they derive. Pipeline constructor methods should only
receive wildcard keyword arguments (e.g. \lstinline{my_pipeline(self, **name_maps)}),
and these arguments should be passed as a dictionary directly to the \emph{name\_maps} argument
of the pipeline initialisation to enable inputs and outputs of the
pipeline to be rerouted to alternative data specifications in modified constructor
methods, typically in subclasses and multi-studies (see
\emph{Extension and specialisation by class inheritance} and \emph{Implementing multi-modal studies}).

@@

Node interfaces are connected to each other, and to inputs and outputs of the pipeline, by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary. The keys of the \emph{inputs} dictionary correspond to
trait names in the node's input interface, whereas the keys of the \emph{outputs} dictionary correspond to
names of entries in the data specification table. The values of both dictionaries are 2-tuples. For pipeline
inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification table
and the format the input data is expected in (i.e. a FileFormat for Fileset specifications or Python datatype for Field specifications).
For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output interface and the format the
output data is generated in. For input connections from other nodes, values of the \emph{inputs} dictionary
consist of a reference to the upstream node and the name of a trait in the
upstream node's output interface (output connections to other nodes are implied by input connections of the receiving nodes).
